Multi sky-view\\ 3D aerosol distribution recovery

### 2013-08-04 article.tex
bookmark

%
% The cleveref package seems very cool but currently it doesn't support hebrew
% (babel) very well, so I just use if for single references.
% As a work around I redefine the number definition as suggested in:
% http://tex.stackexchange.com/questions/118235/using-the-cleveref-package-with-hebrew-and-babel
%
\usepackage[capitalise]{cleveref}
\crefname{section}{Sec.}{Sec.}
\makeatletter
\def\@@number#1{#1}
\makeatother

@@

@@

\bibitem{Martonchik2009}
J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
  properties over land using MISR observations},} in \emph{{Satellite Aerosol
  Remote Sensing over Land,}} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
  Berlin Heidelberg, 2009), pp. 267--293.

@@

We focus on situations where, in addition to air molecules, there is a
single type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\DistUnknown}$ is
variable. As a numerical approximation, assume that within any voxel,
the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$
and the aerosol density $n(k)$ are constants, e.g., corresponding to
the value at each voxel center.  Following \cref{eq:tau}, the optical
depths between the TOA and voxel $k$, and from voxel $k$ to camera $c$
are
% \begin{equation}
%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
%  \label{eq:lSRn}
%\end{equation}
\begin{align}
  \tau_{\rm SR}(k)&= \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \\
  \tau_{{\rm LOS}_c}(k)&= \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
  [\beta^{\rm air}(m)+\sigma^{\rm aerosol} n(m)].
  \label{eq:lSRn}
\end{align}
Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be column
stack vector representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm
  air}(k)$, respectively.  Then, we can write \cref{eq:lSRn} using
matrix notation: \mbox{$\vect{\tau}_{\rm SR}= \OpDistance^{\mathrm{Sun
      \rightarrow voxel}}\vect{\beta}^{\rm air} + \sigma^{\rm
    aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}}
  {\DistUnknown}$},\ and \mbox{$\vect{\tau}_{{\rm LOS}_c}=
  \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air} +
  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel form a
single path from the TOA to camera $c$.  Hence, in matrix notation,
\cref{eq:tau} yields the total optical depths corresponding to LOSs
(of camera $c$) and SRs that cross all voxels:
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;,
  \label{eq:tautotal}
\end{equation}
where ${\bm D}_c= {\bm D}^{\mathrm{Sun \rightarrow voxel}}+ {\bm
  D}^{\mathrm{voxel \rightarrow cam}}_c$ and $\vect{\tau}_c^{\rm air}=
{\bm D}_c \vect{\beta}^{\rm air}$.

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different view-points of a sky that includes {\em
      Haze Blobs}. Images rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
To demonstrate the model, we simulated some scenarios, whose details are as follows.\\
\noindent{\bf Geometry}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$.  Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of $L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm
  B}=255:236:224$.

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we follow
Ref.~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = \sfrac{1} {n^{\rm sealevel}}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}a uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 3.3km; the other is 24km
wide, 2.1km thick and centered at altitude 6.6km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. Fig.~\ref{fig:simulation-results1}a shows one
photographs of the {\em Haze Blobs} scene, as simulated by
Eq.~(\ref{eq:bigIA}).

@@

The MC simulations rely on the same grid as
Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by Monte
    Carlo. [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}, rendered using a MC model.
    [c] Cross section along the $X$-Axis of the MC simulation,
    Single-Scattering simulation and a Single-Scattering image created
    from the reconstructed distribution
    (\cref{sec:optimization-results}).}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
Fig.~\ref{fig:simulation-results1}b shows a photographs of the {\em
  Haze Blobs} scene, derived by the MC process, using \num{10000}
photons per pixel, from the same viewpoint as
Fig.~\ref{fig:simulation-results1}a.  A comparison of a sample
horizontal cross section is shown in \cref{fig:simulation-results1}c.

@@

Sec.~\ref{sec:simul} describes simulates scenes at various grid
resolution.  Depending directly on the area grid finesse, $N_{\rm
  views}$ varied from 12 to 100.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    Single-Scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
We applied the reconstruction algorithm to images created as described
in Secs.~\ref{sec:simul} and~\ref{sec:monte-carlo-simul}. We used the
L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
dedicated to rendering a modeled image. The algorithm was initialized
by ${\bm n}=0$.  Satisfactory convergence occurred in several thousand
iterations. Depending on the resolution it took between minutes to a
couple of hours to complete, in total.

Fig.~\ref{fig:results} shows estimation results, corresponding to the
original distributions of Fig.~\ref{fig:distributions}. In
Figs.~\ref{fig:results}a,b, the single-scattering model was used both
in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}c,d, the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
% Using the recovered distribution shown in Figs.~\ref{fig:results}c
% (originating from MC), we ran the single scattering model to create
% images. \cref{fig:simulation-results1}c shows a cross of such an
% image compared to the original MC image.
Errors in Figs.~\ref{fig:results}a,b stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of Sec.~\ref{sec:inverse-problem}. The total estimation
error can be quantifies based on the $\ell_1$ norm: $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
Figs.~\ref{fig:results}a,b, respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In Figs.~\ref{fig:results}c,d, both cases have
$\epsilon=0.65$.

@@

We thank David~J. Diner for useful discussions. Yoav Schechner is a
Landau Fellow - supported by the Taub Foundation. This work was
conducted in the Ollendorff Minerva Center. Minerva is funded through
the BMBF. Part of this work was per- formed at the Jet Propulsion
Laboratory, California Institute of Technology, under contract with
NASA.

>>>>

%
% The cleveref package seems very cool but currently it doesn't support hebrew
% (babel) very well, so I just use if for single references.
% As a work around I redefine the number definition as suggested in:
% http://tex.stackexchange.com/questions/118235/using-the-cleveref-package-with-hebrew-and-babel
%
\usepackage[capitalise]{cleveref}
\crefname{section}{Sec.}{Secs.}
\makeatletter
\def\@@number#1{#1}
\makeatother

@@

\bibitem{Martonchik2009}
J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
  properties over land using MISR observations},} in \emph{Satellite Aerosol
  Remote Sensing over Land,} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
  Berlin Heidelberg, 2009), pp. 267--293.

@@

@@

We focus on situations where, in addition to air molecules, there is a
single type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\DistUnknown}$ is
variable. As a numerical approximation, assume that within any voxel,
the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$
and the aerosol density $n(k)$ are constants, e.g., corresponding to
the value at each voxel center.  Following \cref{eq:tau}, the optical
depths between the TOA and voxel $k$, and from voxel $k$ to camera $c$
are
% \begin{equation}
%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
%  \label{eq:lSRn}
%\end{equation}
\begin{align}
  \tau_{\rm SR}(k)&= \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \nonumber \\
  \tau_{{\rm LOS}_c}(k)&= \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
  [\beta^{\rm air}(m)+\sigma^{\rm aerosol} n(m)].
  \label{eq:lSRn}
\end{align}
Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be column
stack vector representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm
  air}(k)$, respectively.  Then, we can write \cref{eq:lSRn} using
matrix notation: \mbox{$\vect{\tau}_{\rm SR}= \OpDistance^{\mathrm{Sun
      \rightarrow voxel}}\vect{\beta}^{\rm air} + \sigma^{\rm
    aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}}
  {\DistUnknown}$},\ and \mbox{$\vect{\tau}_{{\rm LOS}_c}=
  \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air} +
  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel form a
single path from the TOA to camera $c$.  Hence, in matrix notation,
\cref{eq:tau} yields the total optical depths corresponding to LOSs
(of camera $c$) and SRs that cross all voxels:
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;,
  \label{eq:tautotal}
\end{equation}
where ${\bm D}_c= {\bm D}^{\mathrm{Sun \rightarrow voxel}}+ {\bm
  D}^{\mathrm{voxel \rightarrow cam}}_c$ and $\vect{\tau}_c^{\rm air}=
{\bm D}_c \vect{\beta}^{\rm air}$.

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
To demonstrate the model, we simulated some scenarios, whose details are as follows.\\
\noindent{\bf Geometry}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$.  Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of $L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm
  B}=255:236:224$.

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we follow
Ref.~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = \sfrac{1} {n^{\rm sealevel}}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}a uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 3.3km; the other is 24km
wide, 2.1km thick and centered at altitude 6.6km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
Eq.~(\ref{eq:bigIA}).

@@

The MC simulations rely on the same grid as
Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}):
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
  \caption{\small [a] Multiple-scattering forward model by Monte
    Carlo. [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}, rendered using a MC model.  [c]
    Cross section along the $X$-Axis of the MC simulation,
    Single-Scattering simulation and a Single-Scattering image created
    from the reconstructed distribution
    (\cref{sec:optimization-results}).}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
Fig.~\ref{fig:mcgrid}b shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as Fig.~\ref{fig:simulation-results1}[left].  A
comparison of a sample horizontal cross section is shown in
\cref{fig:mcgrid}c.

@@

Sec.~\ref{sec:simul} describes simulated scenes at various grid
resolutions.  Depending directly on the area grid finesse, $N_{\rm
  views}$ varied from 12 to 100.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    Single-Scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
We applied the reconstruction algorithm to images created as described
in Secs.~\ref{sec:simul} and~\ref{sec:monte-carlo-simul}. We used the
L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
dedicated to rendering a modeled image. The algorithm was initialized
by ${\bm n}=0$.  Satisfactory convergence occurred in several thousand
iterations. Depending on the resolution it took between minutes to a
couple of hours to complete, in total.

Fig.~\ref{fig:results} shows estimation results, corresponding to the
original distributions of Fig.~\ref{fig:distributions}. In
Figs.~\ref{fig:results}a,b, the single-scattering model was used both
in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}c,d, the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
% Using the recovered distribution shown in Figs.~\ref{fig:results}c
% (originating from MC), we ran the single scattering model to create
% images. \cref{fig:simulation-results1}c shows a cross of such an
% image compared to the original MC image.
Errors in Figs.~\ref{fig:results}a,b stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of Sec.~\ref{sec:inverse-problem}. The total estimation
error can be quantifies by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
The overall mass is recovered, but for 6.5\% loss. For local errors,
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
  In
Figs.~\ref{fig:results}a,b, respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In Figs.~\ref{fig:results}c,d, both cases have
$\epsilon=0.65$.

@@

We thank David~J. Diner for useful discussions. Yoav Schechner is a
Landau Fellow - supported by the Taub Foundation. This work was
conducted in the Ollendorff Minerva Center. Minerva is funded through
the BMBF. Part of this work was performed at the Jet Propulsion
Laboratory, California Institute of Technology, under contract with
NASA.
